Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-09-28 SubGenome Analysis.Rmd
Improved expression plot
Take mean of replicates for each sample, plot all samples instead of only a subset, replace tracking_ids with experiment names.

```{r subgenome_expression_dominance, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=10, fig.height=4, fig.align='center'}
plot <- graphGenePairExpressionsByExperiement(maize.expression.all, homeologs.pairs, 2:12, 1, TRUE)
# plot <- graphGenePairExpressionsByExperiement(maize.expression.all, homeologs.pairs, 2:12, 4, FALSE)
plot(plot)
```

>>>>

```{r subgenome_expression_dominance, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=10, fig.height=6, fig.align='center'}
# plot <- graphGenePairExpressionsByExperiement(maize.expression.all, homeologs.pairs, 2:12, 1, TRUE)
# plot <- graphGenePairExpressionsByExperiement(maize.expression.all, homeologs.pairs, 2:12, 4, FALSE)
plot <- graphGenePairExpressionsByExperiement(maize.expression.sample.avg, homeologs.pairs, 4, FALSE)
plot(plot)
```
